---
title: "Statical Inference Course Project"
output: html_document
---

#### 1. Show where the distribution is centered at and compare it to the theoretical center of the distribution.

```{r}
mns = NULL
for (i in 1 : 1000)
  mns = c(mns, mean(rexp(40, 0.2)))
hist(mns)
```

The distribution is centered at:
```{r}
mean(mns)
```

The theoretical center of the distribution is:
```{r}
lambda <- 0.2
1 / lambda
```

The actual center of the distribution is very close to the theoretical center of the distribution.

#### 2. Show how variable it is and compare it to the theoretical variance of the distribution.

```{r}
vrs = NULL
for (i in 1 : 1000)
  vrs = c(vrs, var(rexp(40, 0.2)))
hist(vrs)
```

The variance of the distribution is:
```{r}
mean(vrs)
```

The theoretical variance of the distribution is:
```{r}
lambda <- 0.2
1 / (lambda ^ 2)
```

The actual variance of the distribution is very close to the theoretical variance of the distribution.

#### 3. Show that the distribution is approximately normal.

Since the exponential(0.2)s are independent and identically distributed, their sum converges to a normal distribution, by the Central Limit Theorem.